Preserving Reciprocal Consistency in Distributed Graph Databases

### 2020-04-06 paper/abstract.tex
more refactoring

\documentclass[sigplan,10pt]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\usepackage{xspace}
\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\usepackage{tikz}
\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage{breqn}

\newcommand{\tDelta}{\textsf{Delta}\xspace}

\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{vertex} = [circle, minimum width=10pt,draw,inner sep=0pt]
\tikzstyle{vertex2} = [circle, minimum width=40pt,draw,inner sep=0pt]
\tikzstyle{server} = [rectangle, rounded corners,minimum width=2cm,minimum height=2.5cm,draw=black]
\tikzstyle{local} = [thick,->,>=stealth]
\tikzstyle{dist} = [thick,dashed,->,>=stealth]
\tikzstyle{node}=[circle,draw,radius=0.3, align=center]

\definecolor{grey}{rgb}{0.52, 0.52, 0.51}
\definecolor{red}{rgb}{0.7, 0.11, 0.11}
\definecolor{blue}{rgb}{0.0, 0.0, 0.55}
\definecolor{green}{rgb}{0.0, 0.42, 0.24}

\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[PaPoC '20]{PaPoC '20: Proceedings of the 7th Workshop on Principles and Practice of Consistency for Distributed Data}{April 27, 2020}{Heraklion, Crete, Greece}
\acmBooktitle{PaPoC '20: Proceedings of the 7th Workshop on Principles and Practice of Consistency for Distributed Data, April 27, 2020, Heraklion, Crete, Greece}
\acmPrice{15.00}
% \acmISBN{978-1-4503-XXXX-X/18/06}

%
% Submission ID.
% Use this when submitting an article to a sponsored event. You'll
% receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

\begin{document}

\title{Preserving Reciprocal Consistency in Distributed Graph Databases}

\author{Jack Waudby}
\email{j.waudby2@ncl.ac.uk}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\author{Paul Ezhilchelvan}
\email{paul.ezhilchelvan@ncl.ac.uk}
\orcid{0000-0002-6190-5685}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\author{Jim Webber}
\email{jim.webber@neo4j.com}
\affiliation{%
  \institution{Neo4j}
  \streetaddress{Union House,182-194 Union Street}
  \city{London}
  \country{UK}
  \postcode{SE1 0LH}}

\author{Isi Mitrani}
\email{isi.mitrani@ncl.ac.uk}
\orcid{0000-0002-7797-7755}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\renewcommand{\shortauthors}{Waudby, et al.}

\begin{abstract}

In our earlier work, we identified \emph{reciprocal consistency} as an important constraint specific to graph databases. If it can be lost even with a negligible small probability, subsequent inconsistent reads followed by writes can corrupt a distributed graph database within a time period extremely short relative to database lifetime. Reciprocal consistency can of course be maintained as a part of enforcing any known isolation guarantee incurring well established performance costs. However, in practice distributed graph databases are often built atop BASE databases with no isolation guarantees, profiting from increased performance but leaving them susceptible to rapid corruption. A lightweight concurrency control protocol ensuring reciprocal consistency is presented, catering for application programmers that are interested in maintaining performance and the structural integrity of their distributed graph database. Protocol performance is evaluated through simulations.
\end{abstract}

% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
% </ccs2012>
% \end{CCSXML}

\ccsdesc[500]{Data Management~Graph Databases}
\ccsdesc[300]{Data Management~Reciprocal Consistency}
\ccsdesc[300]{Data Management~Concurrency Control}

\keywords{Graph Databases, Reciprocal Consistency, BASE}

\maketitle

\input{introduction}

\input{reciprocal-consistency}

\input{dist-graphdb}

\input{corruption}

\input{delta}

\input{modeling}

\input{evaluation}

\input{conclusion}

% \appendix
% \section{Appendix}

% Figure \ref{corruption-again} presents an interleaving when a distributed edge can become half-corrupted under the \tDelta protocol.

% Transaction $T_x$ arrives at $S_i$ at time $t_x$ (let $t=0$) and writes tentatively, with the message delay between servers for $T_x$ to write the edge at $S_j$ being $M_x$. Transaction $T_y$ arrives at $S_j$ at time $t_y$ ($t_y > t_x$) and writes the distributed edge, $T_y$ then takes time $M_y$ to write the edge at $S_i$. If $T_x$ arrives at $S_j$ after $t_y + \Delta$ and $T_y$ arrives at $S_i$ after $t_x + \Delta$ the edge can become half-corrupted. Letting $t_x = 0 $, the probability that $T_x$ and $T_y$ conflict can be formulated as: $$ P \left[ ( T_x >  \Delta + X) \cap (T_y > \Delta-X) \right]$$.

% The arrival times of $T_x,T_y$ are assumed exponentially distributed , $T \sim \exp (\rho)$. Where, $ \rho  = \frac{\lambda P_i}{2N_i}$, the probability a given operation accesses the incorrect record of a half-corrupted edge of type $i$. The transmission times between servers $M_1, M_2 \sim \exp (\delta)$ and are \emph{iid}.

% % Therefore,  $$ g(y) = \delta e^{-\delta y} $$

% Therefore,
% \begin{dmath*}
%   q^{new}_{i} =  {P \left[ ( T_1 >  d + X) \cap (T_2 > d-X)  \right]} \\
%   =  \int_{0}^{d}  \frac{\lambda P_i}{2 N_i} e^{-\frac{\lambda P_i}{2 N_i} x} e^{-\delta (d+x)} e^{-\delta (d-x)} dx + \int_{d}^{\infty} \frac{\lambda P_i}{2 N_i} e^{-\frac{\lambda P_i}{2 N_i} x} e^{-\delta (d+x)} dx  \\
%   =  e^{-2 d \delta} - \left( \frac{\delta}{\frac{\lambda P_i}{2 N_i} + \delta} \right) e^{-(\frac{\lambda P_i}{2 N_i}+ 2\delta)d} \\
% \end{dmath*}

% To choose to bound $\Delta$ consider the probability of the message delay exceeding  $\Delta$.
% \begin{align*}
%   P \left[ M > \Delta \right] & = 1 - e^{- \delta \Delta} \\
%   1 - e^{- \delta \Delta} & = 1 - \epsilon \\
%   e^{- \delta d} & = \epsilon  \\
%   \Delta & = - \frac{\ln(\epsilon)}{\delta}
% \end{align*}

% Substituting $\Delta$ into the above equation yields the conflict probability for a given $\epsilon$. For example, $ e = 0.001$ gives a $0.001$ \% probability the message delay exceeds $\Delta$, for this  $\Delta = 0.035s$
% \begin{align}
%   e^{- \lambda d} =  e^{-\delta d \frac{\lambda}{\delta}} = \epsilon^{\frac{\lambda}{\delta}} \label{eqn7}
% \end{align}
% Therefore, from (\ref{eqn5} and  (\ref{eqn7}),
% \begin{align}
%   & = \epsilon^2 - \frac{\delta}{\frac{\lambda P_i}{2 N_i} + \delta} e^{-\frac{\lambda P_i}{2 N_i} d} \epsilon^2 \\
%   & = \epsilon^2 \left[1 -\frac{\delta}{\frac{\lambda P_i}{2 N_i} + \delta} e^{-\frac{\lambda P_i}{2 N_i} d} \right]
% \end{align}

%Where, $ E \left[ T_1 \right] = E \left[ T_2\right] = \frac{1}{\delta}$.
%Therefore, $$ f(x) =\frac{\lambda P_i}{2N_i} e^{-\frac{\lambda P_i}{2N_i} x} $$

%  =   \int_{0}^{d}  \frac{\lambda P_i}{2 N_i} e^{-\frac{\lambda P_i}{2 N_i} x} e^{-\delta 2 d} dx +  \int_{d}^{\infty} \frac{\lambda P_i}{2 N_i} e^{-\delta d} e^{-(\frac{\lambda P_i}{2 N_i} + \delta)x}  dx  \\
%         =   e^{-2 d \delta} \left[1 - e^{-\frac{\lambda P_i}{2 N_i} d} \right] + \frac{\frac{\lambda P_i}{2 N_i} e^{-\delta d}}{\frac{\lambda P_i}{2 N_i} + \delta} e^{-(\frac{\lambda P_i}{2 N_i} + \delta)d} \\

\bibliographystyle{ACM-Reference-Format}
\bibliography{papoc}

\end{document}
\endinput

>>>>

\begin{abstract}
In our earlier work, we identified \emph{reciprocal consistency} as an important constraint specific to graph databases. If it can be lost even with a negligible small probability, subsequent inconsistent reads followed by writes can corrupt a distributed graph database within a time period extremely short relative to database lifetime. Reciprocal consistency can of course be maintained as a part of enforcing any known isolation guarantee incurring well established performance costs. However, in practice distributed graph databases are often built atop BASE databases with no isolation guarantees, profiting from increased performance but leaving them susceptible to rapid corruption. A lightweight concurrency control protocol ensuring reciprocal consistency is presented, catering for application programmers that are interested in maintaining performance and the structural integrity of their distributed graph database. Protocol performance is evaluated through simulations.
\end{abstract}

### 2020-04-06 paper/commands.tex
more refactoring

\documentclass[sigplan,10pt]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\usepackage{xspace}
\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\usepackage{tikz}
\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage{breqn}

\newcommand{\tDelta}{\textsf{Delta}\xspace}

\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{vertex} = [circle, minimum width=10pt,draw,inner sep=0pt]
\tikzstyle{vertex2} = [circle, minimum width=40pt,draw,inner sep=0pt]
\tikzstyle{server} = [rectangle, rounded corners,minimum width=2cm,minimum height=2.5cm,draw=black]
\tikzstyle{local} = [thick,->,>=stealth]
\tikzstyle{dist} = [thick,dashed,->,>=stealth]
\tikzstyle{node}=[circle,draw,radius=0.3, align=center]

\definecolor{grey}{rgb}{0.52, 0.52, 0.51}
\definecolor{red}{rgb}{0.7, 0.11, 0.11}
\definecolor{blue}{rgb}{0.0, 0.0, 0.55}
\definecolor{green}{rgb}{0.0, 0.42, 0.24}

\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[PaPoC '20]{PaPoC '20: Proceedings of the 7th Workshop on Principles and Practice of Consistency for Distributed Data}{April 27, 2020}{Heraklion, Crete, Greece}
\acmBooktitle{PaPoC '20: Proceedings of the 7th Workshop on Principles and Practice of Consistency for Distributed Data, April 27, 2020, Heraklion, Crete, Greece}
\acmPrice{15.00}
% \acmISBN{978-1-4503-XXXX-X/18/06}

%
% Submission ID.
% Use this when submitting an article to a sponsored event. You'll
% receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

\begin{document}

\title{Preserving Reciprocal Consistency in Distributed Graph Databases}

\author{Jack Waudby}
\email{j.waudby2@ncl.ac.uk}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\author{Paul Ezhilchelvan}
\email{paul.ezhilchelvan@ncl.ac.uk}
\orcid{0000-0002-6190-5685}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\author{Jim Webber}
\email{jim.webber@neo4j.com}
\affiliation{%
  \institution{Neo4j}
  \streetaddress{Union House,182-194 Union Street}
  \city{London}
  \country{UK}
  \postcode{SE1 0LH}}

\author{Isi Mitrani}
\email{isi.mitrani@ncl.ac.uk}
\orcid{0000-0002-7797-7755}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\renewcommand{\shortauthors}{Waudby, et al.}

\begin{abstract}

In our earlier work, we identified \emph{reciprocal consistency} as an important constraint specific to graph databases. If it can be lost even with a negligible small probability, subsequent inconsistent reads followed by writes can corrupt a distributed graph database within a time period extremely short relative to database lifetime. Reciprocal consistency can of course be maintained as a part of enforcing any known isolation guarantee incurring well established performance costs. However, in practice distributed graph databases are often built atop BASE databases with no isolation guarantees, profiting from increased performance but leaving them susceptible to rapid corruption. A lightweight concurrency control protocol ensuring reciprocal consistency is presented, catering for application programmers that are interested in maintaining performance and the structural integrity of their distributed graph database. Protocol performance is evaluated through simulations.
\end{abstract}

% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
% </ccs2012>
% \end{CCSXML}

\ccsdesc[500]{Data Management~Graph Databases}
\ccsdesc[300]{Data Management~Reciprocal Consistency}
\ccsdesc[300]{Data Management~Concurrency Control}

\keywords{Graph Databases, Reciprocal Consistency, BASE}

\maketitle

\input{introduction}

\input{reciprocal-consistency}

\input{dist-graphdb}

\input{corruption}

\input{delta}

\input{modeling}

\input{evaluation}

\input{conclusion}

% \appendix
% \section{Appendix}

% Figure \ref{corruption-again} presents an interleaving when a distributed edge can become half-corrupted under the \tDelta protocol.

% Transaction $T_x$ arrives at $S_i$ at time $t_x$ (let $t=0$) and writes tentatively, with the message delay between servers for $T_x$ to write the edge at $S_j$ being $M_x$. Transaction $T_y$ arrives at $S_j$ at time $t_y$ ($t_y > t_x$) and writes the distributed edge, $T_y$ then takes time $M_y$ to write the edge at $S_i$. If $T_x$ arrives at $S_j$ after $t_y + \Delta$ and $T_y$ arrives at $S_i$ after $t_x + \Delta$ the edge can become half-corrupted. Letting $t_x = 0 $, the probability that $T_x$ and $T_y$ conflict can be formulated as: $$ P \left[ ( T_x >  \Delta + X) \cap (T_y > \Delta-X) \right]$$.

% The arrival times of $T_x,T_y$ are assumed exponentially distributed , $T \sim \exp (\rho)$. Where, $ \rho  = \frac{\lambda P_i}{2N_i}$, the probability a given operation accesses the incorrect record of a half-corrupted edge of type $i$. The transmission times between servers $M_1, M_2 \sim \exp (\delta)$ and are \emph{iid}.

% % Therefore,  $$ g(y) = \delta e^{-\delta y} $$

% Therefore,
% \begin{dmath*}
%   q^{new}_{i} =  {P \left[ ( T_1 >  d + X) \cap (T_2 > d-X)  \right]} \\
%   =  \int_{0}^{d}  \frac{\lambda P_i}{2 N_i} e^{-\frac{\lambda P_i}{2 N_i} x} e^{-\delta (d+x)} e^{-\delta (d-x)} dx + \int_{d}^{\infty} \frac{\lambda P_i}{2 N_i} e^{-\frac{\lambda P_i}{2 N_i} x} e^{-\delta (d+x)} dx  \\
%   =  e^{-2 d \delta} - \left( \frac{\delta}{\frac{\lambda P_i}{2 N_i} + \delta} \right) e^{-(\frac{\lambda P_i}{2 N_i}+ 2\delta)d} \\
% \end{dmath*}

% To choose to bound $\Delta$ consider the probability of the message delay exceeding  $\Delta$.
% \begin{align*}
%   P \left[ M > \Delta \right] & = 1 - e^{- \delta \Delta} \\
%   1 - e^{- \delta \Delta} & = 1 - \epsilon \\
%   e^{- \delta d} & = \epsilon  \\
%   \Delta & = - \frac{\ln(\epsilon)}{\delta}
% \end{align*}

% Substituting $\Delta$ into the above equation yields the conflict probability for a given $\epsilon$. For example, $ e = 0.001$ gives a $0.001$ \% probability the message delay exceeds $\Delta$, for this  $\Delta = 0.035s$
% \begin{align}
%   e^{- \lambda d} =  e^{-\delta d \frac{\lambda}{\delta}} = \epsilon^{\frac{\lambda}{\delta}} \label{eqn7}
% \end{align}
% Therefore, from (\ref{eqn5} and  (\ref{eqn7}),
% \begin{align}
%   & = \epsilon^2 - \frac{\delta}{\frac{\lambda P_i}{2 N_i} + \delta} e^{-\frac{\lambda P_i}{2 N_i} d} \epsilon^2 \\
%   & = \epsilon^2 \left[1 -\frac{\delta}{\frac{\lambda P_i}{2 N_i} + \delta} e^{-\frac{\lambda P_i}{2 N_i} d} \right]
% \end{align}

%Where, $ E \left[ T_1 \right] = E \left[ T_2\right] = \frac{1}{\delta}$.
%Therefore, $$ f(x) =\frac{\lambda P_i}{2N_i} e^{-\frac{\lambda P_i}{2N_i} x} $$

%  =   \int_{0}^{d}  \frac{\lambda P_i}{2 N_i} e^{-\frac{\lambda P_i}{2 N_i} x} e^{-\delta 2 d} dx +  \int_{d}^{\infty} \frac{\lambda P_i}{2 N_i} e^{-\delta d} e^{-(\frac{\lambda P_i}{2 N_i} + \delta)x}  dx  \\
%         =   e^{-2 d \delta} \left[1 - e^{-\frac{\lambda P_i}{2 N_i} d} \right] + \frac{\frac{\lambda P_i}{2 N_i} e^{-\delta d}}{\frac{\lambda P_i}{2 N_i} + \delta} e^{-(\frac{\lambda P_i}{2 N_i} + \delta)d} \\

\bibliographystyle{ACM-Reference-Format}
\bibliography{papoc}

\end{document}
\endinput

>>>>

% commands
\renewcommand\thesubfigure{(\alph{subfigure})}
\newcommand{\tDelta}{\textsf{Delta}\xspace}

% tikz
\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{vertex} = [circle, minimum width=10pt,draw,inner sep=0pt]
\tikzstyle{vertex2} = [circle, minimum width=40pt,draw,inner sep=0pt]
\tikzstyle{server} = [rectangle, rounded corners,minimum width=2cm,minimum height=2.5cm,draw=black]
\tikzstyle{local} = [thick,->,>=stealth]
\tikzstyle{dist} = [thick,dashed,->,>=stealth]
\tikzstyle{node}=[circle,draw,radius=0.3, align=center]

% colours
\definecolor{grey}{rgb}{0.52, 0.52, 0.51}
\definecolor{red}{rgb}{0.7, 0.11, 0.11}
\definecolor{blue}{rgb}{0.0, 0.0, 0.55}
\definecolor{green}{rgb}{0.0, 0.42, 0.24}

### 2020-04-06 paper/main.tex
more refactoring

\usepackage{xspace}
\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\usepackage{tikz}
\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage{breqn}

\newcommand{\tDelta}{\textsf{Delta}\xspace}

\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{vertex} = [circle, minimum width=10pt,draw,inner sep=0pt]
\tikzstyle{vertex2} = [circle, minimum width=40pt,draw,inner sep=0pt]
\tikzstyle{server} = [rectangle, rounded corners,minimum width=2cm,minimum height=2.5cm,draw=black]
\tikzstyle{local} = [thick,->,>=stealth]
\tikzstyle{dist} = [thick,dashed,->,>=stealth]
\tikzstyle{node}=[circle,draw,radius=0.3, align=center]

\definecolor{grey}{rgb}{0.52, 0.52, 0.51}
\definecolor{red}{rgb}{0.7, 0.11, 0.11}
\definecolor{blue}{rgb}{0.0, 0.0, 0.55}
\definecolor{green}{rgb}{0.0, 0.42, 0.24}

@@

%
% Submission ID.
% Use this when submitting an article to a sponsored event. You'll
% receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

@@

\author{Jack Waudby}
\email{j.waudby2@ncl.ac.uk}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\author{Paul Ezhilchelvan}
\email{paul.ezhilchelvan@ncl.ac.uk}
\orcid{0000-0002-6190-5685}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

\author{Jim Webber}
\email{jim.webber@neo4j.com}
\affiliation{%
  \institution{Neo4j}
  \streetaddress{Union House,182-194 Union Street}
  \city{London}
  \country{UK}
  \postcode{SE1 0LH}}

\author{Isi Mitrani}
\email{isi.mitrani@ncl.ac.uk}
\orcid{0000-0002-7797-7755}
\affiliation{%
  \institution{Newcastle University}
  \city{Newcastle}
  \country{UK}
  \postcode{NE4 5TG}
}

@@

\begin{abstract}

In our earlier work, we identified \emph{reciprocal consistency} as an important constraint specific to graph databases. If it can be lost even with a negligible small probability, subsequent inconsistent reads followed by writes can corrupt a distributed graph database within a time period extremely short relative to database lifetime. Reciprocal consistency can of course be maintained as a part of enforcing any known isolation guarantee incurring well established performance costs. However, in practice distributed graph databases are often built atop BASE databases with no isolation guarantees, profiting from increased performance but leaving them susceptible to rapid corruption. A lightweight concurrency control protocol ensuring reciprocal consistency is presented, catering for application programmers that are interested in maintaining performance and the structural integrity of their distributed graph database. Protocol performance is evaluated through simulations.
\end{abstract}

>>>>

\usepackage{xspace}
\usepackage[labelformat=simple]{subcaption}
\usepackage{tikz}
\usepackage{fancyvrb}
\usepackage{xcolor}
\usepackage{breqn}

@@

% Submission ID.
% Use this when submitting an article to a sponsored event. You'll
% receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

@@

\input{authors}

@@

\input{abstract}
